### 2014-03-15 src/discussion.Rnw
Fix up the discussion a little bit

%\begin{figure}[t]
%\includegraphics[totalheight=4.5cm]{fig/opstrat1.pdf}
%\caption{Mutant distribution in a sample project along operators and program elements}
%\label{fig:egmutants}
%\end{figure}

%Our data from Figure~\ref{fig:op} suggests that while there are small differences, the average rate of detection of mutants of each type is similar to the average number of mutants produced for each type. This suggests that mutants produced by each operator is similar in terms of difficulty of detection.

We see a few patterns in our results. The first is that sampling strategy
can predict the final score with very minimal loss in accuracy up to a fraction
of $\frac{1}{64}$ of the total number of mutants (Our experiments suggest up
to $70$ times reduction, with a low standard deviation of $6.72$). We did not
cut off with the 99\% rule as mentioned by Zhang et al.~\cite{zhang2013ase}
(Originally proposed by Offutt et al.~\cite{offutt1996experimental} for a
different measurement), and instead chose to observe that we obtained
$R^2 > 0.96$ which provides a high confidence in the accuracy of prediction.

@@

% There may in fact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
% It is a representation of the distribution of mutants along two orthogonal axes --- the
% mutation operators, and program elements such as classes. For the purposes of this
% explanation, assume that each classes contain equal number of lines, and each mutant
% produced per line by each of the mutation operators are marked by a small solid circle.
% The two solid vertical lines in blue and red represents two classes, one with a relatively
% small number of mutants and other with large number of mutants. Consider that we are sampling
% by class, and we are choosing all mutants for simplicity. Let $c$ be the number of classes.
% Here, a mutant in red class contributes to $1/n_{red}$ to the mean of the score of the
% red class, and the red class contributes $1/c$ to the total mean.  So the contribution of a
% mutant in red class to the complete is $1/(c * n_{red})$. Similarly for blue class.
% However, if the sampling is done on a complete project basis, then the contribution of any
% mutant is $\frac{1}{\sum_{i=1}^{c} n_{i}}$, which depending on the size of the class might
% be different from what it would contribute if sampling is used. To put it another way,
% for any kind of sampling used based on sub elements, the units in the sample gets equal
% weightage in contribution irrespective of the size of elements themselves, while if the sampling
% is done on a project basis, the contribution of sub elements depends on the number of mutants
% each elements produced.
% 
% What this is saying in effect is that irrespective of the sophestication of sampling used,
% the simplest sampling technique --- that of project based sampling --- is the best form of
% sampling, for a representative set.
% 
% This also applies immediately to operator selection as it is another kind of sampling on
% a smaller set. Hence it is no surprise that for larger samples, random sampling is able
% to trump operator selection on predicting the final result.
%

>>>>

From our data, we see that for original and generated test suites, the
mutant reduction ratio and standard deviation was similar for stable strategies
(where the standard deviation of the reduction achieved was less than half
of the reduction achieved). This suggests that our analysis is equally
applicable for both generated test suites and original test suites.

Analysing the scores achieved further, we note that the accuracy of prediction
($R^2$) achieved by sampling is generally lower for generated test
suites. Especially, as the fraction of sampling becomes larger the accuracy
reduces drastically for generated test suites while the accuracy still
holds good for original test suites
Secondly, we also observe that the multiplier factor $\beta_1$ 
is smaller for generated test suites than original test suites. This
observation holds good for all sampling and operator selection strategies
examined.  Both these factors together suggest that generated
test suites have a higher variability in their sampled mutation scores than
original test suites. We note that since $\beta_1$ was generally smaller
for generated test suites than original test suites, the full mutation score
corresponding to a sampled mutation score for generated test suites would
be lower than what would be expected from original test suite.
Secondly, the amount of reduction that can be gained by sampling satisfying
a given accuracy is lower for generated test suites in comparison with original
test suites.

Considering different sampling strategies, we see a few general patterns. The
first is that sampling strategy can predict the final score with very
minimal loss in accuracy up to a fraction of $\frac{1}{64}$ of the total
number of mutants (Our experiments suggest up to $70$ times reduction,
with a low standard deviation of $6.72$). We did not cut off with the 99\%
rule as mentioned by Zhang et al.~\cite{zhang2013ase} (Originally proposed
by Offutt et al.~\cite{offutt1996experimental} for a different measurement),
and instead chose to observe that we obtained $R^2 > 0.96$ which provides
a high confidence in the accuracy of prediction.

@@
